Universidade Federal de Santa Catarina - UFSC

### 2017-04-23 monograph/proposal/main.tex
Update the Times New Roman package to newtxtext & newtxmath.
Fixed some table warnings for the monograph/proposal/main.tex

% To use the font Times New Roman, instead of the default LaTeX font
\usepackage{mathptmx}

@@

@@

    \noindent\makebox[\textwidth]{%
    \resizebox{1.1\linewidth}{!}{%
    % \setlength\tabcolsep{1.0pt}
    \begin{tabular}{|
                     *1{>{\RaggedRight\arraybackslash}p{4.0cm}|} % Riscos
                     *3{>{\RaggedRight\arraybackslash}p{0.9cm}|} % Probabilidade, Impacto, Prioridade
                     *2{>{\RaggedRight\arraybackslash}p{4.0cm}|} % Resposta, Prevenção
                    }
    \hline Riscos  & Pro\-ba\-bi\-li\-da\-de & Im\-pac\-to & Prio\-ri\-da\-de & Es\-tra\-té\-gia de res\-pos\-ta & Ações de pre\-ven\-ção \\ \hline

@@

    \hline \end{tabular}
    }%
    }%

>>>>

% To use the font Times New Roman, instead of the default LaTeX font
% \usepackage{mathptmx}
%
% more up-to-date than 'mathptmx'
\usepackage{newtxtext,newtxmath}

@@

% Use its macro adjustwidth* to extend tables out of outer text border.
% https://tex.stackexchange.com/questions/366155/how-to-write-a-table-a-little-larger-than-the-paragraphs-with-centered-columns
\usepackage[strict]{changepage}

@@

    % https://tex.stackexchange.com/questions/366156/how-to-change-the-left-padding-for-one-latex-tables-cell
    % https://tex.stackexchange.com/questions/366155/how-to-write-a-table-a-little-larger-than-the-paragraphs-with-centered-columns
    %
    \begin{adjustwidth}{-0.5\marginparwidth}{-0.5\marginparwidth}
    \small
    \begin{tabularx}{\linewidth}
    {|
        *1{                 >{\RaggedRight\arraybackslash\hsize=1.1\hsize }X       |} % Riscos
        *3{@{\hspace{3.0pt}}>{\Centering\arraybackslash                   }p{0.9cm}|} % Probabilidade, Impacto, Prioridade
        *2{                 >{\RaggedRight\arraybackslash\hsize=0.95\hsize}X       |} % Resposta, Prevenção
    }

    \hline Riscos  & Pro\-ba\-bi\-li\-da\-de & Im\-pac\-to & Prio\-ri\-da\-de & Es\-tra\-té\-gia de res\-pos\-ta & Ações de pre\-ven\-ção \\ \hline

@@

    \hline \end{tabularx}
    \end{adjustwidth}
